Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-02-09 paper.tex
Add paragraph on impact of flute instability on heating

\rev{Since the flute instability only develops nonlinearly when using anisotropic viscosity, it is difficult to distinguish the effect of the instability from that of the viscosity itself on the viscous or Ohmic heating. \todo{finish this paragraph}}

>>>>

\rev{It is difficult to distinguish the effect of the flute instability on the viscous or Ohmic heating from that of the viscosity itself, particularly since the flute instability is quickly disrupted by the kink instability. However, it can be concluded from the plots of cumulative heat (Figures~\ref{fig:heating-4} and~\ref{fig:heating-3}) that the majority of the viscous and Ohmic heat is generated by the nonlinear development of the kink instability. There is additionally some non-negligible Ohmic heating which is generated prior to the onset of the kink, however this is attributed to the large-scale currents associated with the twist in the field, rather than any currents created by the flute instability. This leads us to conclude that the flute instability itself has little direct impact on coronal heating, but instead can affect the heating rate by slowing the development of the kink instability.}
